### 2017-07-19 README.Rmd
Add timing examples for flights data

```
mtcars %>%
  specify(mpg ~ hp) %>% # alt: response = mpg, explanatory = cyl
  hypothesize(null = "independence") %>% # or "slope = 0"
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "slope")
```

>>>>

```
mtcars %>%
  specify(mpg ~ hp) %>% # alt: response = mpg, explanatory = cyl
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "slope")
```

### 2017-07-19 examples/profiles_examples.Rmd
Add timing examples for flights data

### Hypothesis tests
![h-test diagram](figs/ht-diagram.png)

@@

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% 
  dplyr::sample_n(size = 500) %>% 
  dplyr::mutate(frisco = dplyr::case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  dplyr::select(age, sex, frisco, drugs, height, status)
```

- `height` and `age` are numerical variables.
- `sex` has two categories (`"m"`, `"f"`)
- `frisco` has two categories (`"san fran"`, `"not san fran"`)
- `drugs` has three categories (`"never"`, `"sometimes"`, `"often"`) - Also has missing values
- `status` has three categories (`"single"`, `"available"`, `"seeing someone"`)

@@

```{r}
prof_small %>%
  specify(sex ~ frisco) %>% # alt: response = sex, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = frisco
  hypothesize(null = "point", 
              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = frisco
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "F") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>% # or "slope = 0"
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(sex ~ frisco) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

>>>>

### Hypothesis tests
![h-test diagram](../figs/ht-diagram.png)

@@

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% 
  dplyr::sample_n(size = 500) %>% 
  dplyr::mutate(city = dplyr::case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  dplyr::select(age, sex, city, drugs, height, status)
```

- `height` and `age` are numerical variables.
- `sex` has two categories (`"m"`, `"f"`)
- `city` has two categories (`"san fran"`, `"not san fran"`)
- `drugs` has three categories (`"never"`, `"sometimes"`, `"often"`) - Also has missing values
- `status` has three categories (`"single"`, `"available"`, `"seeing someone"`)

@@

```{r}
prof_small %>%
  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "F") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

@@

```{r}
prof_small %>%
  specify(sex ~ city) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

### 2017-07-19 examples/timing_flights_5k.Rmd
Add timing examples for flights data

---
output:
  github_document
params:
  num_rows: 10000
  rep_times: 1000
---

@@

This analysis is for `r params$num_rows` flights with `reps =` ``r params$rep_times``.

>>>>

---
output:
  github_document:
    toc: true 
    toc_depth: 3
params:
  num_rows: 5000
  rep_times: 5000
---

@@

This analysis is for `r params$num_rows` flights with `reps =```r params$rep_times``.
